---
title: "Untitled"
output: html_document
---


```{r}

---
title: "SHiny_2"
output: html_document
---

```{r}
library(DT)
library(shiny)
library(tidyverse)
library(sf)
library(sp)
library(leaflet)

#Reads in eviction dataset and creates a date column of type dates. 
data= read.csv("./nycdb/weekly_202203070957.csv")
data$my_dates = as.Date(data$`day`, '%Y-%m-%d')


#Reads in anotger dataset that has zipcodes and latitude, longitude information
zipcode_polygons = st_read("./ZIP_CODE_040114/ZIP_CODE_040114.shp")  %>%
  select(ZIPCODE, geometry, POPULATION)
#Reads in another dataset that has only zipcodes, count by zipcodes of the eviction table.
cases = read.csv("./UPDATES_CASES.csv")%>%
  mutate(date = as.Date(filedate), zipcode = substr(zipcode, 0, 5))
#Get healthdata set from github
health_data <- read.csv(url("https://raw.githubusercontent.com/nychealth/coronavirus-data/master/latest/last7days-by-modzcta.csv"))

neigborhouds = health_data %>%
              select(modzcta, modzcta_name)
colnames(neigborhouds)[1] <- "ZipCode"
#neigborhouds$Location = paste(neigborhouds$ZipCode,neigborhouds$modzcta_name, sep = "<br/>")


getEvinctionTable = function(start_date, end_date){
  filtered_cases = cases %>%
    filter(date >= start_date & date <= end_date)  %>%
    group_by(zipcode)  %>%
    summarize(count = sum(totaleviction)) 
  
  tables_output = neigborhouds %>%
    merge(filtered_cases, by.x = "ZipCode", by.y = "zipcode") %>%
    arrange(desc(count))
}

#create a function that maps the evictions
getEvinctionMap = function(start_date, end_date){
  #creates a dataframe between the given date range and also groups them by zipcode and and sums up the evictions
  filter_cases = cases %>%
    filter(date >= start_date & date <= end_date)  %>%
    group_by(zipcode)  %>%
    summarize(count = sum(totaleviction))
  #joins both the zipcode dataset and the eviction dataset
  zipcode_cases = zipcode_polygons  %>%
    merge(filter_cases, by.x = "ZIPCODE", by.y = "zipcode")
  #creates a map 
  return (ggplot() +
          geom_sf(data = zipcode_cases,
          aes(fill = count), size = 0.2) +
          scale_fill_continuous(low="yellow",high="red",
                                name = paste("Evinctions by Zipcode between", startDate, " and ", endDate)) +
                                coord_sf(crs = "EPSG:2263",
                                default_crs = "EPSG:4326") +
                                theme_void())
}

  
  

  getEvinctionLeafletMap = function(start_date, end_date){
    
    filter_cases = cases %>%
    filter(date >= start_date & date <= end_date)  %>%
    group_by(zipcode)  %>%
    summarize(count = sum(totaleviction))
    
    zipcode_cases = zipcode_polygons  %>%
    merge(filter_cases, by.x = "ZIPCODE", by.y = "zipcode")
  labels <- sprintf("<strong>%s</strong><br/>%s cases",
                  zipcode_cases$ZIPCODE, zipcode_cases$count) %>%
                  lapply(htmltools::HTML)
  pal <- colorBin(palette = "OrRd", 9, domain = zipcode_cases$count)
  
  
    return (zipcode_cases %>%
    st_transform(crs = "+init=epsg:4326")%>%
    leaflet(options = leafletOptions(minZoom = 11, maxZoom = 16))%>%
    setMaxBounds(-73.97, 40.77,-73.97, 40.77) %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(label = labels,
                stroke = FALSE,
                smoothFactor = .5,
                opacity = 1,
                fillOpacity = 0.7,
                fillColor = ~ pal(zipcode_cases$count),
                highlightOptions = highlightOptions(weight = 5,
                                                    fillOpacity = 1,
                                                    color = "black",
                                                    opacity = 5,
                                                    bringToFront = TRUE)))
  }
 

getEvinction = function(start_date, end_date, borough){
  data %>% 
  select(my_dates, active_cases, cases_filed, city) %>% 
  filter(my_dates > start_date & my_dates <end_date & city == borough) %>% 
  ggplot(aes(x= my_dates, group =1)) +   
  geom_line(aes(y = active_cases), color = "red") + 
  geom_line(aes(y = cases_filed), color="steelblue")  + 
  scale_x_date(date_breaks = '4 month', guide = guide_axis(n.dodge = 2), date_labels = "%m-%y") 
}
# Define UI for app that draws a histogram ----
ui <- fluidPage(
  
  # App title ----
  titlePanel("Eviction in New York City!"),
  
  # Sidebar layout with input and output definitions ----
  sidebarLayout(
    
    # Sidebar panel for inputs ----
    sidebarPanel(
      
      # Input: Slider for the number of bins ----
      selectInput(inputId = "city", 
               label = "Choose a County", 
                choices = c("New York", "Brooklyn"), 
                plotOutput("distPlot")),
      
      sliderInput(inputId = "input_date", 
                label = "Scroll to select your dates",
                timeFormat="%Y-%m",
                min = as.Date(min(data$my_dates)),
                max = as.Date(max(data$my_dates)),
                value = c(as.Date("2018-02-01"),as.Date("2020-01-01"))
                )
      
      
    ),
    
    # Main panel for displaying outputs ----
    mainPanel(
      
      # Output: Histogram ----
      plotOutput(outputId = "distPlot"),
      leafletOutput(outputId = "mapPlot"),
      DT::dataTableOutput("table")
    )
  )
)




# Define server logic required to draw a histogram ----
server <- function(input, output) {
  
  

  output$distPlot <- renderPlot({
    getEvinction(input$input_date[1], input$input_date[2], input$city)
  })
  #output$mapPlot <- renderPlot({
  #  getEvinctionMap(input$input_date[1], input$input_date[2]) 
  #})
  output$mapPlot <- leaflet::renderLeaflet({
    getEvinctionLeafletMap(input$input_date[1], input$input_date[2]) 
  })
  output$table <- DT::renderDataTable(datatable({
    datas = getEvinctionTable(input$input_date[1], input$input_date[2])
    
  }))
  
}


# Create Shiny app ----
shinyApp(ui = ui, server = server)

```





```
